Linear Ordered Attribute Grammar scheduling using SAT-solving

### 2014-10-16 paper/paper.tex
Remove some comments

Apart from the fact that this translation to SAT helps in efficiently (in practice) solving the scheduling problem, there also is another benefit: it is now possible to encode extra constraints on the resulting schedule. We show two \Jeroen{de 2e moet nog uitgewerkt worden} scheduling optimisations that are interesting from an attribute grammar perspective, for which the optimal schedule can be found efficiently by expressing the optimisation in the SAT problem.

@@

In order to encode this we also construct a \emph{nonterminal dependency graph}. This graph contains all attributes that are defined for the corresponding nonterminal and the edges in this graph must define a total order\Thomas{Actually it can be partial, which is also what we obtain using a variable for every inherited x synthesized pair. For example, an interface with only 1 visit (and multiple inherited or synthesized attributes) defines a partial order since we don't care about the order between inherited/synthesized attributes in the same visit. The visit-sequences that are calculated in the end do imply a total order however.}\Jeroen{Yes, but it can also just be total, which is much easier to explain, and I think this detail doesn't matter here} on the attributes. Furthermore, the edges in the nonterminal dependency graph should agree with the (indirect) dependencies from the production dependency graphs such that no cycles exist.

>>>>

Apart from the fact that this translation to SAT helps in efficiently (in practice) solving the scheduling problem, there also is another benefit: it is now possible to encode extra constraints on the resulting schedule. We show two scheduling optimisations that are interesting from an attribute grammar perspective, for which the optimal schedule can be found efficiently by expressing the optimisation in the SAT problem.

@@

In order to encode this we also construct a \emph{nonterminal dependency graph}. This graph contains all attributes that are defined for the corresponding nonterminal and the edges in this graph must define a total order on the attributes. Furthermore, the edges in the nonterminal dependency graph should agree with the (indirect) dependencies from the production dependency graphs such that no cycles exist.
